---
title: "ADHD rx and suicide multinational"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    code_folding: hide
    df_print: paged
    
  pdf_document: default
---

1. Main analysis

```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(readxl)
risk<-read_excel("D:/enter/4_bouken/2024_4 ADHD Suicide/R/risk_results.xlsx")
library(meta)

risk_main<-subset(risk, Analysis=="main" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=risk_main$Case_inc,
                 event.c=risk_main$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")
main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))

```
```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(readxl)
rp<-read_excel("D:/enter/4_bouken/2024_4 ADHD Suicide/R/riskperiod_results.xlsx")


library(meta)
rp$IRR<-as.numeric(rp$IRR)
rp$IRRLCI<-as.numeric(rp$IRRLCI)
rp$IRRUCI<-as.numeric(rp$IRRUCI)
rp$Case_inc<-as.numeric(rp$Case_inc)
rp$Control_inc<-as.numeric(rp$Control_inc)
rp$Case_total<-as.numeric(rp$Case_total)
rp$Control_total<-as.numeric(rp$Control_total)


rp_main_pre90<-subset(rp, Analysis=="Main" & `Risk Window`=="90 days before ADHD medication initiation")
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",byvar = `Risk Window`,
                 title = "Main analysis", subgroup =  `Risk Window`)
library(forestplot)
library(dplyr)



main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
          leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(readxl)
rp<-read_excel("D:/enter/4_bouken/2024_4 ADHD Suicide/R/riskperiod_results.xlsx")

#Spittal, M.J., Pirkis, J. & Gurrin, L.C. Meta-analysis of incidence rate data in the presence of zero events. BMC Med Res Methodol 15, 42 (2015). https://doi.org/10.1186/s12874-015-0031-0

library(meta)
rp$IRR<-as.numeric(rp$IRR)
rp$IRRLCI<-as.numeric(rp$IRRLCI)
rp$IRRUCI<-as.numeric(rp$IRRUCI)
rp$Case_inc<-as.numeric(rp$Case_inc)
rp$Control_inc<-as.numeric(rp$Control_inc)
rp$Case_total<-as.numeric(rp$Case_total)
rp$Control_total<-as.numeric(rp$Control_total)


rp_main_pre90<-subset(rp, Analysis=="Main" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 leftcols=c("studlab", "event.e", "n.e", "event.c", "n.c"),
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis", subgroup =  `Risk Window`)


library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
                leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="Main" & `Risk Window`=="Subsequent ADHD medication use")
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
   #              subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis", subgroup =  `Risk Window`)
library(forestplot)
library(dplyr)



main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

2. Subgroup: Stimulants

```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


risk_main<-subset(risk, Analysis=="stim" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))

```
```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="Stimulants" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)



main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="Stimulants" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)






```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="Stimulants" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)



```

3. Subgroup: Non-stimulants


```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


risk_main<-subset(risk, Analysis=="nons" )

m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=risk_main$Case_inc,
                 event.c=risk_main$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")
main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```

```{r fig.height=4, fig.width=9, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="Non-stimulants" & `Risk Window`=="90 days before ADHD medication initiation" )

m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,8),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=9, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="Non-stimulants" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,8),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=9, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="Non-stimulants" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,8),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)



```


4. Subgroup: male

```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

risk_main<-subset(risk, Analysis=="subm" )

m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=risk_main$Case_inc,
                 event.c=risk_main$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")
main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))
```
```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="Sub_male" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)




```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="Sub_male" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)






```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="Sub_male" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)



```

5. Subgroup: female

```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


risk_main<-subset(risk, Analysis=="subf" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))

```
```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="Sub_female" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)



main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="Sub_female" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)

main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)






```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="Sub_female" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)



```
6. Sensitivity 1: Recurrent suicide


```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


risk_main<-subset(risk, Analysis=="sen1" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_1" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="SA_1" & `Risk Window`=="First 90 days of ADHD medication use")
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)




```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_1" & `Risk Window`=="Subsequent ADHD medication use" & IRR!=0)
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)



```

3. Sensitivity 2: Remove people with death


```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


risk_main<-subset(risk, Analysis=="sen2" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_2" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="SA_2" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_2" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

3. Sensitivity 3: Extend exposure duration by 1 week:
```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
risk_main<-subset(risk, Analysis=="sen3" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```


```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_3" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)


rp_main_pre90<-subset(rp, Analysis=="SA_3" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)





```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_3" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

Sensitivity 4: Extend exposure duration by 5 weeks:
```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
risk_main<-subset(risk, Analysis=="sen4" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```


```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_4" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
rp_main_pre90<-subset(rp, Analysis=="SA_4" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_4" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```
Sensitivity 5: Extend exposure duration by 10 weeks:
```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
risk_main<-subset(risk, Analysis=="sen5" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```


```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_5" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
rp_main_pre90<-subset(rp, Analysis=="SA_5" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_5" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

Sensitivity 6: Only inlcude people wtih ADHD dx
```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
risk_main<-subset(risk, Analysis=="sen6" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```


```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```

Sensitivity 7: Removing people with ADHD Rx 12 months before observation start
```{r fig.height=3, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
risk_main<-subset(risk, Analysis=="sen7" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRR_Lower),
                 upper=log(IRR_Upper),
                 studlab = Country,
                 data = risk_main,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "DL",
                 title = "Main analysis")

main<-forest(m.gen,    
       col.square="cornflowerblue",
                 title = "Overall",
        ff.heading = "bold",
col.i.inside.square="black",
#col.study = "red",
       col.study = "black",col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="navy",
       lab.e=NULL, lab.c=NULL,
label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ))


```


```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="90 days before ADHD medication initiation" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}
library(meta)
rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="First 90 days of ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL",
                 title = "Main analysis")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)

```

```{r fig.height=4, fig.width=8.7, message=FALSE, warning=FALSE}

library(meta)

rp_main_pre90<-subset(rp, Analysis=="SA_6" & `Risk Window`=="Subsequent ADHD medication use" )
m.gen <- metagen(TE = log(IRR),
                 lower=log(IRRLCI),
                 upper=log(IRRUCI),
                 studlab = Country,
                 data = rp_main_pre90,
                 event.e=rp_main_pre90$Case_inc,
                 event.c=rp_main_pre90$Control_inc,
                 n.e=Case_total,
                 n.c=Control_total,
                 sm = "IRR",
                 fixed = FALSE,
                 random = TRUE,
                 subgroup=`Risk Window`,
                 method.tau = "DL")
library(forestplot)
library(dplyr)
main_pre90<-forest(m.gen,    
       col.square="cornflowerblue",
        ff.heading = "bold",
col.i.inside.square="black",
       col.diamond.random = "darkblue",
       col.diamond.lines = "black",
       col.diamond.lines.random = "black",
       xlim = c(0.2,5),
       col.by="black",
       lab.e=NULL, lab.c=NULL, label=T,
         leftcols = c("studlab", "n.e", "n.c"),
       leftlabs=c("Country","Exposed \n person-years","Unexposed \n person-years" ),
       rightlabs=c("(IRR)","95% CI","Weight" ),
overall.hetstat=F,  test.subgroup=F)


```
